---
title: "DAV"
author: "Siddhesh, Akkshay, Girish, Akhil"
date: "27 April 2019"
output:
  html_document: default
  pdf_document: default
---


Importing the Black Friday Dataset and importing the libraries

```{r}
library(readr)
library(tidyverse)
library(ggplot2)
BlackFriday <- read.csv("C:/Users/siddh/Desktop/Rutgers Spring 19/DAV/BlackFriday.csv", header=TRUE)
View(BlackFriday)
bf<-BlackFriday
head(BlackFriday)

```


EXPLORATORY DATA ANALYSIS


#count the number of male and female customers in the data set

```{r}
bf %>% filter(Gender == "F") %>% nrow()
bf %>% filter(Gender == "M") %>% nrow()
```

As we can see from the above result, we have 132,197 Females and 405,380 males.



#count the number of married and unmarried customers in the data set
```{r}
bf %>% filter(Marital_Status==1) %>% nrow()
bf %>% filter(Marital_Status==0) %>% nrow()
```

As we can see from the above result, we have 219760 married and 317817 unmarried customers.


```{r}
bf %>% group_by(Marital_Status) %>% summarize(purchase_amount = sum(as.numeric(Purchase))) %>% ggplot(mapping = aes(x = factor(Marital_Status), y = purchase_amount, fill = factor(Marital_Status))) + geom_col() + theme_bw()

```



```{r}
attach(BlackFriday)

BlackFriday  %>% group_by(Age, Gender) %>% summarize(purchase_amount = sum(as.numeric(Purchase))) %>% ggplot(mapping = aes(x = factor(Age), y = purchase_amount, fill = Gender)) + geom_col() + theme_bw()

```



```{r}
temp<-subset(bf, !duplicated(Occupation))
temp1<-temp$Occupation
temp1
tab<-table(temp1)
tab
```

From this we can see there are 21 occupations. Now let's create a graph depending on the occupations.


```{r}
data3 <- bf %>% group_by(Occupation) %>% summarize(purchase_amount = sum(as.numeric(Purchase)))
ggplot(data3, mapping = aes(x = factor(Occupation), y = purchase_amount, fill = factor(Occupation))) + geom_col() + theme_bw()


```


LINEAR REGRESSION : 


```{r}
str(bf)
model<-lm(Purchase~. -User_ID -Product_ID, data=bf)
summary(model)

```


As from above, we find out marital status is insignicifant, we remove the column.





```{r}
smp_size <- floor(0.75 * nrow(BlackFriday))
set.seed(123)
train_ind <- sample(seq_len(nrow(BlackFriday)), size = smp_size)
train_set <- BlackFriday[train_ind,c(3:7,10:12)]

names(train_set)
test_set <- BlackFriday[-train_ind, ]
y_test<-as.data.frame(test_set[,12], drop=false)
names(y_test)<-c("purchase")
test_set<-as.data.frame(test_set[,c(3:7,10:11)], drop=false)


model1<-lm(Purchase~., data=train_set)
summary(model1)
```


```{r}

summary(model)
pred<-predict(model1,newdata = test_set)
pred1<-na.omit(pred)
head(pred1,100)

```





#In the model summary above, we can notice interesting findings. During Black Friday, Males make purchases by 319.478$ more than the Female do (which is an intercept here). Also, people of age between 51-55 make more $1025.9 more purchases than the teenagers of age between 0 and 17. Not to mention the fact that people of 51-55 age have overall spent more money then others.By looking at all categories, we can see that 51-55 is the "maximum" point of purchase age. Below 51, by age the purchase ammount also increases, and after 55+ there is a decline again   





#RMSE is 4630$, which is too high, that's why this model is not a good one for doing any predictions. The same thing we can say looking at R-adjusted. 
#Dataset's independent Variables cannot predict Purchase variable accurately.





```{r}
library(ggplot2)
ggplot(model1, aes(x = Age, y = Purchase)) + 
  geom_boxplot() + 
  ggtitle("Purchase amounts by Age")
```

#Our conclusions regarding Age and Purchase relations is confirmed by the boxplot. As we can see, there is slight difference among the ages and the 51-5 age is in top of them. However, the diference is not significant. Now let's look at gender



```{r}
ggplot(model1, aes(x = Gender, y = Purchase)) + 
  geom_boxplot() + 
  ggtitle("Purchase am
          ounts by Gender")
```

#The boxplot confirmes our previous asummption that males spend more on black fridays than females, but again with no significant difference






